### 2019-06-17 2-Chapters/1-Chapter/chapter1.tex
Fixed a typo in Ch2, and better outline for Ch1

\TODOL{Ecrire les 1.1 et 1.2 en quelques pages}

@@

% Two ways communications
However, this kind of mono-directional wireless communications were soon found to not be satisfactory for many applications, and thus bi-directional standards were defined from the $1910$s.
First developed by and for the military, and the navy (\eg, the Titanic sent the first SOS signal over radio in $1912$),
such applications have reached general public usage since the $1950$s.
The greatest achievement of this long-running R\&D domain was the avent of mobile telephony in the $1990$s, which has continued to be more and more present in people lives in the richer countries in the world, with the booming of cellphones since the $2000$s and smartphones since the $2010$s.
In most systems, there is still an antenna in charge of a large area (or cell), and many devices are able to receive and transmit data to the antenna.
Nowadays, the most well-known systems include WiFi, and systems deployed for mobile phone communications, with a long list of standards from 1G, 2G, 3G, 4G and now 5G, still in development in $2019$.
Even if both systems initially differed in usage, as 1G was designed to exchange only voice, and WiFi to link wireless devices at home to an Internet-connected box, they are conceptually very close.
As the systems are cellular, any device knows the antenna (or base station) it is associated with, and the bi-directional nature of their exchanges makes a centralized control possible.
In order to optimize the efficiency of the network, the base station is equipped with decision making algorithms that affects the devices in the cell to the available resources (time slots, RF bands, power etc).
To be able to communicate with the base station without interfering with each others, such affectation should be orthogonal, and led to systems based on Time Division Multiple Access (TDMA) and Frequency Division Multiple Access (FDMA), or more recently to Non-Orthogonal techniques (NOMA).
Traditionally, the base station aimed only at maximizing the Quality of Service (QoS), that englobes the data rate, latency, availability and other measures of performance of the wireless communications to and from the devices.
More recently, green radio has emerged as a solution to the tradeoff between maximizing QoS while minimizing the power consumption of base stations and devices.

% The opposite: decentralized broadcasting, and the age of IoT
Finally, a third kind of systems are of the opposite kind, and can be designed as decentralized broadcasting: an antenna is still in charge of many devices, but such devices can only send up-link packets, and the only down-link data they can receive are short acknowledgements sent from the base-station to indicate success or failure of an up-link packet.
This family of wireless systems are referred to as Internet of Things,
and a typical example of application is for sensor networks.

For the future development of smart grids, smart cities, smart homes, or smart agriculture, sensor networks are promised to be widely deployed.
Two examples of future applications that are already in deployment, in France or other countries, are connected buildings and connected agriculture.
For buildings, the main goal is to reduce the cost of heating empty buildings and use temperature sensor networks to get accurate and regular data about the temperature in each room and each floor, and let the centralized heat control optimize its cost and energy consumption.
For agriculture, one example can be to equipped every cow (in large farms) with a sensors that emits biological information, such as body temperature or stress level etc, in order to optimize the time of milking and monitors the health of the animals.

% OK commencer par un paragraphe qui explique qu'on étudie les télécom dans le but de les rendre automatiquement plus efficace, plus verte, plus adaptative

This third kind of wireless systems are characterized by their decentralized nature: due to the really limited information that the base station can send to the devices, it is no longer possible to optimize the efficiency of the network from the centralized point-of-view of the base station.
In the present and future IoT networks, many devices of heterogenous nature are using the same antenna for many different applications.
A common hypothesis is that such IoT devices have a strong constraint on their power consumption, as most of them will be deployed without a direct power access and will use a battery, which duration should be maximized (typically more than 10 years).
Another common constraint for IoT devices is their low duty cycle, as most applications target one to a few messages sent by day, in strike opposition to the high data-rate pursued for centralized systems such as 4G/5G and WiFi.

@@

@@

% Modified from the https://draw.io/ map from
% https://github.com/trekhleb/homemade-machine-learning/blob/master/images/machine-learning-map.xml
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.90\textwidth]{machine-learning-map.pdf}
\caption{Classification of the main types of Machine Learning: MAB is a subset of Reinforcement Learning and RL is a subset of ML.}
\label{fig:1:MainTypesOfMachineLearning}
\end{figure}

We illustrate this idea in the following Figure~\ref{fig:1:ReinforcementLearningCycle}, where a player (or learner) interacts with its environment by taking an action $A(t)$ (\eg, a choice in a finite set, $A(t)\in\{1,\dots,K\}$, or a vector $A(t)\in\R^d$,) and then observing a reward $r(t)$, which is a certain measure of success from the environment (\eg, $r(t)\in\{0,1\}$ for binary failure/success, or $r(t)\in\R$).
The goal of the player is to maximize its reward.
Many real-world problems can be framed as Reinforcement Learning problems \cite{bouneffouf2019survey}, for instance learning to walk or to drive, learning to play a game, or discovering which treatment is efficient in healing a certain disease.

@@

More precisely, in this thesis we focus on a certain kind of Reinforcement Learning models where the learning does not have access to the entire reaction of the environment after taking its action.
In other words, we focus on RL with limited feedback, when the player only sees the reward given by its action at every round, and not the reward that would have been given if she chose any other action.
This kind of limited feedback is called \emph{bandit information}, and we discuss the history and the concept of \emph{Multi-Armed Bandits} in details in the next Chapter~\ref{chapter:2}.
% Il faut expliquer ce que c'est que les bandits, rapidement, et leur application à l'OSA

@@

\textbf{The spectrum scarcity issue.}
%
% FIXME how to explain spectrum scarcity?
A major problem of current wireless technologies is the issue of spectrum scarcity:
in most kinds of frequency bands, the entire RF spectrum is now allocated and free bands no longer exist, limiting the possibility of adding new usage.
%
% FIXME copy paste from Wikipedia
% Traditional regulatory structures have been built for an analog model and are not optimized for cognitive radio.
Regulatory bodies in the world, like the Federal Communications Commission in the United States, as well as different independent measurement campaigns found that most radio frequency spectrum was inefficiently utilized
meaning that while a band can be allocated to a certain usage, it can be free from any user in certain time and/or place.
For instance, see \cite{valenta2010survey} for a survey on spectrum utilization in Europe.
%
Cellular network bands are overloaded in most parts of the world, but other frequency bands (such as military, amateur radio and paging frequencies) are insufficiently utilized.
Independent studies performed in some countries confirmed that observation, and concluded that spectrum usage highly depends on time and place.
Moreover, fixed spectrum allocation prevents rarely used frequencies (those assigned to specific services) from being used, even when any unlicensed users would not cause noticeable interference to the assigned service.
Regulatory bodies in the world have been considering whether to allow unlicensed users in licensed bands if they would not cause any interference to licensed users.
These initiatives have focused cognitive-radio research on \textbf{Dynamic Spectrum Access (DSA)}.

% explain PU and SU in a few sentences
In licensed bands, there are Primary Users (PU) paying to access the network, for instance anybody has to pay to have a mobile phone number and use the mobile telephony network.
The PU have a strict priority over any other non-paying users, referred to as Secondary User (SU).
So even though the RF bands are allocated, real world measurements often show that some bands are not densely used, and thus if a SU is equipped with an efficient sensing capacity, it can analyze its environment, and use a licensed band if it is free of any PU.
% explain DSA
This defines the concept of DSA was thus proposed in the early $2000$s, and we refer to the survey \cite{Zhao07} for more details.
% FIXME how to explain OSA ?
We focus on one example, the \textbf{Opportunistic Spectrum Access}.

@@

\paragraph{Previous work in the SCEE team.}

@@

\paragraph{Current challenges.}
%
quels nouveaux challenges en 2016 ?

@@

\paragraph{Our approach.}
%
directions de recherches

- réfléchir aux modèles, quelles hypothèses sont retirées comparé au modèle OSA

- analyser mathématiquement les modèles

- proposer des solutions : algorithmes, dont la convergence est justifiée, ou heuristiques

- des simulations logicielles

- des démonstrations matérielles

- et en bonus on obtient aussi de belles contributions théoriques

@@

\TODOL{Je dois faire ça d'ici mercredi matin}
% Je peux m'inspirer beaucoup de la thèse de Navik...
% https://tel.archives-ouvertes.fr/tel-01668536/document

\paragraph{On Cognitive Radio.}

@@

\paragraph{On Multi-Armed Bandit.}

\paragraph{Applications for Opportunistic Spectrum Access.}
% Detail the previous work from our team SCEE on bandits + OSA : Wassim, Navik

@@

\TODOL{Je sais pas à quel point je veux parler de la thèse de Navik? Peut-être que j'en aurai dit assez au Chapitre 1, et que là ça suffira..}
In a second PhD thesis supervised by Christophe Moy \cite{Modi17PhD}, Navikkumar Modi studied the impact
of using MAB algorithms to optimize channel selection
on the battery life of a wireless device.
On the one hand, running a MAB algorithm such as UCB-like algorithms was proven to be useful and can bring significant improvement in terms of successful transmission rates, directly increasing the battery life of the device.
On the other hand, classical MAB algorithms tend to switch arms a lot of times, especially in the beginning of the learning process, and this induces a lot of dynamical hardware reconfiguration for the wireless device, as selecting a different channel requires a change in the radio hardware used by the device.
Each hardware reconfiguration costs energy for the device, and quickly switching algorithms will lead to a reduction of the battery life.
The tradeoff between the two aspects is studied empirically in
\cite{modiDemo2016}.
%
Another interesting works is \cite{Modi17QoS}.

@@

\subsection{Example: decentralized learning in unlicensed bands with selfish or orthogonalization-based MAB algorithms}

@@

@@

>>>>

\TODOL{Ecrire les 1.1 et 1.2 en quelques pages}
\TODOL{J'enlève l'abstract et la minitoc dès que le chapitre est terminé !}

@@

% Two ways communications
However, this kind of mono-directional wireless communications were soon found to not be satisfactory for many applications, and thus bi-directional standards were defined from the $1910$s.
First developed by and for the military, and the navy (\eg, the Titanic sent the first SOS signal over radio in $1912$),
such applications have reached general public usage since the $1950$s.
The greatest achievement of this long-running R\&D domain was the avent of mobile telephony in the $1990$s, which has continued to be more and more present in people lives in the richer countries in the world, with the booming of cellphones since the $2000$s and smartphones since the $2010$s.
In most systems, there is still an antenna in charge of a large area (or cell), and many devices are able to receive and transmit data to the antenna.
Nowadays, the most well-known systems include WiFi, and systems deployed for mobile phone communications, with a long list of standards from 1G, 2G, 3G, 4G and now 5G, still in development in $2019$.
Even if both systems initially differed in usage, as 1G was designed to exchange only voice, and WiFi to link wireless devices at home to an Internet-connected box, they are conceptually very close.
As the systems are cellular, any device knows the antenna (or base station) it is associated with, and the bi-directional nature of their exchanges makes a centralized control possible.
In order to optimize the efficiency of the network, the base station is equipped with decision making algorithms that affects the devices in the cell to the available resources (time slots, RF bands, power etc).
To be able to communicate with the base station without interfering with each others, such affectation should be orthogonal, and led to systems based on Time Division Multiple Access (TDMA) and Frequency Division Multiple Access (FDMA), or Non-Orthogonal techniques only started to emerge recently (\eg, NOMA).
Traditionally, the base station aimed only at maximizing the Quality of Service (QoS), that englobes the data rate, latency, availability and other measures of performance of the wireless communications to and from the devices.
More recently, green radio has emerged as a solution to the tradeoff between maximizing QoS while minimizing the power consumption of base stations and devices.

% The opposite: decentralized broadcasting, and the age of IoT
Finally, a third kind of systems are of the opposite kind, and can be designed as decentralized broadcasting: an antenna is still in charge of many devices, but such devices can only send up-link packets, and the only down-link data they can receive are short acknowledgements sent from the base-station to indicate success or failure of an up-link packet.
This family of wireless systems are referred to as Internet of Things,
and a typical example of application is for sensor networks.\\
\indent
For the future development of smart grids, smart cities, smart homes, or smart agriculture, sensor networks are promised to be widely deployed.
Two examples of future applications that are already in deployment, in France or other countries, are connected buildings and connected agriculture.
For buildings, the main goal is to reduce the cost of heating empty buildings and use temperature sensor networks to get accurate and regular data about the temperature in each room and each floor, and let the centralized heat control optimize its cost and energy consumption.
For agriculture, one example can be to equipped every cow (in large farms) with a sensors that emits biological information, such as body temperature or stress level etc, in order to optimize the time of milking and monitors the health of the animals.\\
%
% OK commencer par un paragraphe qui explique qu'on étudie les télécom dans le but de les rendre automatiquement plus efficace, plus verte, plus adaptative
\indent
This third kind of wireless systems are characterized by their decentralized nature: due to the really limited information that the base station can send to the devices, it is no longer possible to optimize the efficiency of the network from the centralized point-of-view of the base station.
In the present and future IoT networks, many devices of heterogenous nature are using the same antenna for many different applications.
A common hypothesis is that such IoT devices have a strong constraint on their power consumption, as most of them will be deployed without a direct power access and will use a battery, which duration should be maximized (typically more than 10 years).
Another common constraint for IoT devices is their low duty cycle, as most applications target one to a few messages sent by day, in strike opposition to the high data-rate pursued for centralized systems such as 4G/5G and WiFi.

@@

\TODOL{Citer \cite{Toledano2014EnglishSummary,Toledano2014FrenchFull} et dire les trucs suivants}
To quote a report published by the French government, ``Dynamic Spectrum Management For Innovation And Growth'' \cite{Toledano2014EnglishSummary,Toledano2014FrenchFull}:
\begin{quote}
    In France, digital economy represents $5\%$ of GDP and affects $80\%$ of the French economy.
    Radio frequencies are essential to many sectors: communications, broadcasting, transportation, satellite networks, energy networks and smart grids, public or private security, defense, etc.
    %
    Everyone agrees on the growing need for spectrum.
    This growing need results from two phenomena.
    On the one hand, mobile traffic should be multiplied by 13 to 25 fold between 2011 and 2017.
    On the other hand, the development of new innovative services such as the Internet of Things and its multiple applications (smart cities, e-health...), could lead to a growing number of connected devices, up to 50 billion in 2020, according to estimations.
    Today, there are no more available frequencies in the easily exploitable frequency bands.
    Moreover, it is getting more and more difficult to resort to classical methods of frequency bands liberation.
    Growing recourse to spectrum sharing, and in particular dynamic spectrum sharing, constitutes an important spectrum reserve.
    A particular sharing form, the use of unlicensed bands, open to all and free, has been intensely developed with the growth of Wifi use.
\end{quote}

@@

% Modified from the https://draw.io/ map from
% https://github.com/trekhleb/homemade-machine-learning/blob/master/images/machine-learning-map.xml
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.95\textwidth]{machine-learning-map.pdf}
\caption{Classification of the main types of Machine Learning: MAB is a subset of Reinforcement Learning and RL is a subset of ML.}
\label{fig:1:MainTypesOfMachineLearning}
\end{figure}

We illustrate this idea in the following Figure~\ref{fig:1:ReinforcementLearningCycle}, where a player (or learner) interacts with its environment by taking an action $A(t)$ (\eg, a choice in a finite set, $A(t)\in\{1,\dots,K\}$, or a vector $A(t)\in\R^d$,) and then observing a reward $r(t)$, which is a certain measure of success from the environment (\eg, $r(t)\in\{0,1\}$ for binary failure/success, or $r(t)\in\R$).
The goal of the player is to maximize its reward, by trials and errors (\ie,actions and rewards).
Many real-world problems can be framed as Reinforcement Learning problems \cite{bouneffouf2019survey}, for instance learning to walk or to drive, learning to play a board or computer game, or discovering which treatment is efficient in healing a certain disease.

@@

% Il faut expliquer ce que c'est que les bandits, rapidement, et leur application à l'OSA
More precisely, in this thesis we focus on a certain kind of Reinforcement Learning models where the learning does not have access to the entire reaction of the environment after taking its action.
In other words, we focus on RL with limited feedback, when the player only sees the reward given by its action at every round, and not the reward that would have been given if she chose any other action.
This kind of limited feedback is called \emph{bandit information}, and we discuss the history and the concept of \emph{Multi-Armed Bandits} in details in the next Chapter~\ref{chapter:2}.
Clinical trials and treatment discovery was historically the first application of MAB, in $1933$ with the early work of W. Thompson \cite{Thompson33}.

@@

\textbf{The spectrum scarcity issue.}
%
A major problem of current wireless technologies is the issue of spectrum scarcity:
in most kinds of frequency bands, as illustrated in Figure~\ref{fig:1:United_States_Frequency_Allocations_Chart_2016_The_Radio_Spectrum} below, the entire RF spectrum is now allocated and free bands no longer exist, limiting the possibility of adding new usage.
%
% FIXME copy paste from Wikipedia, change a little bit!
% Traditional regulatory structures have been built for an analog model and are not optimized for cognitive radio.
Regulatory bodies in the world, like the Federal Communications Commission in the United States, as well as different independent measurement campaigns found that most radio frequency spectrum was inefficiently utilized
meaning that while a band can be allocated to a certain usage, it can be free from any user in certain time and/or place.
For instance, see \cite{valenta2010survey} for a survey on spectrum utilization in Europe.
%
Cellular network bands are overloaded in most parts of the world, but other frequency bands (such as military, amateur radio and paging frequencies) are insufficiently utilized.
Independent studies performed in some countries confirmed that observation, and concluded that spectrum usage highly depends on time and place.
Moreover, fixed spectrum allocation prevents rarely used frequencies (those assigned to specific services) from being used, even when any unlicensed users would not cause noticeable interference to the assigned service.
Regulatory bodies in the world have been considering whether to allow unlicensed users in licensed bands if they would not cause any interference to licensed users.
These initiatives have focused cognitive-radio research on \textbf{Dynamic Spectrum Access (DSA)}.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.65\textwidth]{United_States_Frequency_Allocations_Chart_2016_The_Radio_Spectrum.pdf}
    \caption{A chart representing the allocation of radio spectrum in the United States of (North) America, in $2016$. \copyright{} Wikimedia.}
    % https://upload.wikimedia.org/wikipedia/commons/c/c7/United_States_Frequency_Allocations_Chart_2016_-_The_Radio_Spectrum.pdf?uselang=fr
    \label{fig:1:United_States_Frequency_Allocations_Chart_2016_The_Radio_Spectrum}
\end{figure}

% explain PU and SU in a few sentences
In licensed bands, there are Primary Users (PU) paying to access the network, for instance anybody has to pay to have a mobile phone number and use the mobile telephony network.
The PU have a strict priority over any other non-paying users, referred to as Secondary User (SU).
So even though the RF bands are allocated, real world measurements often show that some bands are not densely used, and thus if a SU is equipped with an efficient sensing capacity, it can analyze its environment, and use a licensed band if it is free of any PU.
% explain DSA
This defines the concept of DSA was thus proposed in the early $2000$s, and we refer to the survey \cite{Zhao07} for more details.
We focus on one example, the \textbf{Opportunistic Spectrum Access} (OSA).

\TODOL{Je dois faire ça d'ici mercredi matin}

% FIXME how to explain OSA ?
\paragraph{Opportunistic Spectrum Access.}
%

@@

\paragraph{Previous work in the SCEE team on OSA.}

@@

\paragraph{New challenges for the IoT networks.}
%
quels nouveaux challenges en 2016 ?

@@

@@

% Je peux m'inspirer beaucoup de la thèse de Navik...
% https://tel.archives-ouvertes.fr/tel-01668536/document

@@

% Detail the previous work from our team SCEE on bandits + OSA : Wassim, Navik

@@

In a second PhD thesis supervised by Christophe Moy \cite{Modi17PhD}, Navikkumar Modi studied the impact
of using MAB algorithms to optimize channel selection
on the battery life of a wireless device.
On the one hand, running a MAB algorithm such as UCB-like algorithms was proven to be useful and can bring significant improvement in terms of successful transmission rates, directly increasing the battery life of the device.
On the other hand, classical MAB algorithms tend to switch arms a lot of times, especially in the beginning of the learning process, and this induces a lot of dynamical hardware reconfiguration for the wireless device, as selecting a different channel requires a change in the radio hardware used by the device.
Each hardware reconfiguration costs energy for the device, and quickly switching algorithms will lead to a reduction of the battery life.
The tradeoff between the two aspects is studied empirically in
\cite{modiDemo2016}.

@@

@@

We start by formulating the problem studied in this thesis, and then we develop our approach.

\paragraph{Problematic.}
%
\begin{quote}
    \emph{``Can we adapt the decision making tools already successfully applied to Cognitve Radio for Opportunistic Spectrum Access to the specific needs of CR for the future IoT networks''}
\end{quote}

We answered partially to this problematic by the following research steps.

\paragraph{Part I.}

FIXME
We explored the rich literature of multi-armed bandits.
Many algorithms exist.
So we have to understand which ones can be applied to CR and IoT.

Our exploration of the large number of MAB algorithms, and of MAB models, developed in the recent literature has produced a Python library of simulation of MAB problems.
%
We wrote the most exhaustive open-source simulation library for MAB problems, called SMPyBandits, which is published online under an open-source licence \cite{SMPyBandits,SMPyBanditsJMLR}.
We present in details its architecture and its features in Chapter~\ref{chapter:3}, along with different examples of its usage.
A full documentation is available online, as well as exhaustive instructions to reproduce the experiments used in the rest of this thesis.

Because there are so many different MAB algorithms, we are also interested by the question of how practitioner can chose the one she will implement in a given IoT object.
FIXME online algorithm selection and aggregation, with our contribution \Aggr{}.

\paragraph{Part II.}
%

First model \cite{Bonnefoi17}, CROWNCOM paper, model to detail

Verify this first model empirically: proof of concept \cite{Besson2018ICT}

Second model with decision making also for the retransmissions of packets \cite{Bonnefoi2019WCNC}

Selfish

Understand Selfish in the simpler framework of multi-player MAB

In the OSA setting, we failed

But we proposed new algorithms for this problem, and relaunched the research on this model \cite{Besson2018ALT}

% \paragraph{Our approach.}
% %
% directions de recherches

% - réfléchir aux modèles, quelles hypothèses sont retirées comparé au modèle OSA

% - analyser mathématiquement les modèles

% - proposer des solutions : algorithmes, dont la convergence est justifiée, ou heuristiques

% - des simulations logicielles

% - des démonstrations matérielles

% - et en bonus on obtient aussi de belles contributions théoriques

% FIXME c'est bon tout ce qu'on a avant ?

@@

\newpage % WARNING

### 2019-06-17 2-Chapters/2-Chapter/chapter2.tex
Fixed a typo in Ch2, and better outline for Ch1

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proven to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses modified versions of the indexes of \klUCB$^+$ for arms that are not sampled much (see \cite{Honda2019} for more details), and of MOSS$^+$ for the other arms.
If the two indexes
% $U^{\KLUCB+}_k(t)$ and $U^{\mathrm{MOSS}+}_k(t)$
are defined by
$U^{\mathrm{MOSS}+}_k(t) & \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \log\left(T / (K N_k(t))\right) / N_k(t)} \right)$
and
$U^{\KLUCB+}_k(t) & \eqdef \sup\limits_{q \in [0,1]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \log(T / (K N_k(t))) / N_k(t) \right\}$,
and if $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch uses the index defined as follows:
\begin{align*}
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) & \eqdef \begin{cases}
        U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\end{align*}
%

>>>>

More recently, the \klUCB-switch from \cite{Garivier18} is the first algorithm to be proven to
enjoy simultaneously a distribution-free regret bound of optimal order $\sqrt{KT}$, and a distribution-dependent regret bound of optimal order as well, that is, matching the $C_I \ln(T)$ lower bound by \cite{LaiRobbins85}.
It is an index policy that uses modified versions of the indexes of \klUCB$^+$ for arms that are not sampled much (see \cite{Honda2019} for more details), and of MOSS$^+$ for the other arms.
If the two indexes
% $U^{\KLUCB+}_k(t)$ and $U^{\mathrm{MOSS}+}_k(t)$
are defined by
$U^{\mathrm{MOSS}+}_k(t) \eqdef \frac{X_k(t)}{N_k(t)} + \max\left(0, \sqrt{ \log\left(T / (K N_k(t))\right) / N_k(t)} \right)$
and
$U^{\KLUCB+}_k(t) \eqdef \sup\limits_{q \in [0,1]} \left\{ q : \kl\left(\frac{X_k(t)}{N_k(t)}, q\right) \leq \log(T / (K N_k(t))) / N_k(t) \right\}$,
and if $f(T, K) = \lfloor (T/K)^{\gamma}\rfloor$ for $\gamma=1/5$,
then \klUCB-switch uses the index defined as follows:
\begin{align*}
    U^{\klUCB\text{-}\mathrm{switch}}_k(t) & \eqdef \begin{cases}
        U^{\KLUCB+}_k(t) & \text{if } N_k(t) \leq f(T, K), \\
        U^{\mathrm{MOSS}+}_k(t) & \text{if } N_k(t) > f(T, K).
    \end{cases}.
\end{align*}
%
